Generality in food webs scales with species richness, not latitude

### 2015-05-12 manuscript/coverletter.tex
First paragraph roughed out

We believe that our study

>>>>

We believe that our study will be of general interest to the readership of \emph{\myjournal}} because it deals with the general scaling relationships between the distribution of trophic interactions within a community, species richness, and latitude. We assess these relationships both across several ecosystem types and over different trophic levels. Our results will therefore be applicable to researchers working with a wide variety of study systems and focal species.

[[A second paragraph going into more detail]]
